Behavior Driven Development in Haskell

### 2012-06-02 paper.tex
remove TBD impl of wouldThrow
BCP: section description

\begin{quote}
    TBD: The implementation of \verb|shouldThrow| may still be
    interesting.  We can describe it, if we have time left.
\end{quote}

\begin{quote}
\small
\begin{verbatim}
shouldThrow ::
  Exception e => IO a -> Selector e -> Assertion
\end{verbatim}
\end{quote}

@@

\begin{quote}
    TBD: in this section we:
    \begin{itemize}
        \item We show how to do BDD in Haskell
        \item How to reuse pieces of specification
        \item How to use Doctest and Hspec with Cabal's test feature
    \end{itemize}
\end{quote}

>>>>

@@

In this section we show how to do BDD in Haskell, how to reuse pieces
of specification, and how to use Doctest and Hspec in combination with
Cabal's test feature.
